Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-08-10 volunteer-clouds-ieee-ci-si.tex
A ver qué os parecen las conclusiones
Miradlas @fergunet @mariosky @pacastillo. También conviene revisar a fondo. Voy a intentar mandarlo mañana o pasado.

>>>>

The second objective of this paper was to model the user behavior in a
first attempt to try and predict performance. As should be expected,
the model depends on the implementation, with contributions following
a General Extreme Values distribution in the case of {\sf NodIO} and a
Weibull distribution for {\sf NodIO$^2$}. These distributions are
close enough to each other and, in the second case, reflect the fact
that all time spent in the page is actually devoted to computing,
which is why the time spent (represented by the number of
contributions to the pool) follows a model quite similar to that found
for games or other online activities. The reverse might be true: if we
want to have returning users for the experiments, it is probable that
we should {\em gamify} the experience so that once they've done it
once, they might do it more times. In the spirit of Open Science, this
gamification might involve computing in real time data such as the one
presented in this paper and showing it in the same page.

In general, linking and finding correlations between user choices and
performance is an interesting avenue to explore in the future. Even if
the three previous experiments were published in a similar, way, one
obtained up to 5 times more total cycles  that the one with the least
number of cycles. It is also essential to obtain volunteers as
simultaneously as possible, so it is possible that the features of the
social network in terms of real-time use will also play a big
role. Even as it is difficult to create controlled experiments in this
area, it is an interesting challenge to explore in the future.

Although we think that, in general, the results presented in this
paper are independent of the problem chosen, it is true that even if
it a difficult problem for evolutionary algorithms, it takes a few
seconds with the right settings to solve. This makes it difficult also
for this kind of asynchronous framework, but it would be interesting
to check the performance for more computationally demanding
tasks. Besides, the two versions of the framework include as an
algorithmc variant using random population size. We do not think this
has had a big influence on the result, but it would be interesting to
measure exactly what this influence has been. Adding a bit of more
control to the user might contribute also to gamification. Right now
the user has only two webworkers. It is a matter of a single click to
open more tabs in the browser, giving more webworkers, but it would be
interesting to put everything in a single page and under our control,
to check how often this happens and under which conditions.

Finally, the implementation needs some refinement in terms of
programming and also ease of use. Tools such as Yeoman might be used
to create a generator in which the user just has to create a fitness
function, with the rest of the framework wrapped around
automatically. All this, as the data used for this paper and the paper
itself, will be published with a free license in GitHub.
